Toxic Code Snippets on Stack Overflow

### 2018-11-18 cloverflow-tse/cloverflow.tex
+ Updated the paper to reflect the response letter. + Small typo fix in the response letter. + Update a few wording in the response letter.

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
\begin{abstract}
Online code clones are code fragments that are copied from software projects or
online sources to Stack Overflow as examples. Due to an absence of a checking
mechanism after the code has been copied to Stack Overflow, they can become
toxic code snippets, e.g.,~they suffer from being outdated or violating the
original software license. We present a study of online code clones on Stack
Overflow and their toxicity by incorporating two developer surveys and a
large-scale code clone detection. A survey of 201 high-reputation Stack Overflow
answerers (33\% response rate) showed that 131 participants (65\%) have ever
been notified of outdated code and 26 of them (20\%) rarely or never fix the
code. 138 answerers (69\%) never check for licensing conflicts between their
copied code snippets and Stack Overflow's CC BY-SA 3.0. A survey of 87 Stack
Overflow visitors shows that they experienced several issues from Stack Overflow
answers: mismatched solutions, outdated solutions, incorrect solutions, and buggy code. 
85\% of them are not aware of CC BY-SA 3.0
license enforced by Stack Overflow, and 66\% never check for license conflicts
when reusing code snippets. Our clone detection found online clone pairs between
72,365 Java code snippets on Stack Overflow and 111 open source projects in the
curated Qualitas corpus. We analysed 2,289 non-trivial online clone candidates.
Our investigation revealed strong evidence that 153 clones have been copied from
a Qualitas project to Stack Overflow. We found 100 of them (66\%) to be outdated
and potentially harmful for reuse. Furthermore, we found 214 code snippets that
could potentially violate the license of their original software and appear 7,112
times in 2,427 GitHub projects.

@@

%The popularity of the Internet encourages tremendous amount of source code
% being shared online.
Stack Overflow is a popular online programming community with 7.6 million users,
14 million questions, and 23 million answers\footnote{Data as of 21 August 2017
	from~\url{https://stackexchange.com/sites}}. It allows programmers to ask
questions and give answers to programming problems. The website has found to be
useful for software
development~\cite{Ponzanelli2013,Ponzanelli2014,Keivanloo2014,Park2014,
	Stolee2014,Subramanian2013,Diamantopoulos2015,Treude2016} and also valuable for
educational purposes~\cite{Nasehi2012}. On Stack Overflow, each conversation
contains a question and a list of answers. The answers frequently contain at
least one code snippet as a solution to the question asked. We found that the
code snippets are usually not authored directly on the Stack Overflow website
but copied from another location. A snippet in an answer could be copied and
modified from a code snippet in the question, copied from the answerer's own
code or from other locations including open source software (OSS) systems.

@@

Toxic code snippets mean code snippets that, after incorporating into software, degrades the software quality.
Stack Overflow code snippets
cloned from open source software or online sources can become toxic when they
are (1)~outdated, (2)~violating their original software
license, (3) exhibiting code smells, or (4) having security vulnerabilities. 
In this study, we focus on the first two forms of toxic code snippets, outdated code and license-violating code,
as these two problems are still underexplored compared to code smells~\cite{Tufano2015} and vulnerabilities~\cite{Acar2016,Fischer2017}.
Moreover, Stack Overflow users also express their concerns about these two problems
as shown in several discussion threads\footnote{Discussions about outdated answers and code license on
	Stack Overflow: meta.stackexchange.com/questions/131495, 
	meta.stackexchange.com/questions/11705/, meta.stackexchange.com/questions/12527,
	meta.stackexchange.com/questions/25956, meta.stackoverflow.com/questions/321291.}
	 on \textsf{meta.stackexchange.com} about outdated
answers and license of code on Stack Overflow.
Outdated code snippets can be harmful since they are not up-to-date with their originals and may
contain defects. Code snippets from open source projects usually fall under a
specific software license, e.g.,\ GNU General Public License (GPL). If they are
cloned to Stack Overflow answers without the license, and then flow to other projects
with conflicting licenses, legal issues may occur.

@@

	\item \textbf{An investigation of toxic code snippets on Stack Overflow:} Our study shows that from
	the 2,289 online clones, at least 328 have been copied from open source
	projects or external online sources to Stack Overflow, potentially violating
	software licenses. For 153 of them, we found evidence that they have been copied
	from a specific open source project. 100 of them were found to be outdated. %
	% and questionable for being reused.

@@

Moreover, using the information in git commit messages, we can associate each
change to its respective issues in an issue tracking system, such as Bugzilla or
Jira. We found that in 58 cases, the cloned code snippets on Stack Overflow were
changed because of a request in the issue tracking system. Since issue tracking
systems are also used, besides bug reports, for feature request and feature
enhancements, having an issue tracking ID can reflect that most of the changes are important
and not only a superficial fix such as code formatting. The intent behind
the changes are grouped into six categories as shown in \Cref{tab:intent_outdated}.
Enhancement is the majority intent accounting for 65 of the 100 outdated code (65\%), followed 
by code deprecation (15\%). There were 10 outdated code snippets (10\%) caused by bug fixing.
The rest of the changes are because of code refactoring (6\%), changing coding style (3\%), and 
the data format change (2\%).
Not all outdated code is toxic. However, the 10 buggy and outdated code snippets 
we found are toxic and are harmful to reuse.

@@

\textbf{Internal validity:} 
We applied different mechanisms to ensure the validity of the clone pairs we
classified.  First, we used two widely-used clone detection tools, Simian and
SourcererCC.  We tried five other clone detectors but could not add them to the
study due to their scalability issues and susceptibility to incomplete code
snippets. We adopted Bellon's agreement metric~\cite{Bellon2007} to merge clone
pairs for the manual classification and avoid double counting of the same clone
pairs. We studied the impact of choosing different thresholds for Bellon's clone agreement and the minimum clone
size of the two clone detectors and selected the optimal values.
Nevertheless, our study might still suffer from false negatives,
i.e.,~online code clones that are not reported by the tools or are filtered out
by the size (less than 10 lines) within the clone detection process. We selected
accepted answers on Stack Overflow in this study to focus on code snippets that
solve the question's problem and are often shown on top of the answer list.
We investigated the 72,365 Stack Overflow code snippets used in our study and
found that 62,245 of them (86\%) are also the highest voted answers.
%While most of the time they are also the highest voted answers, some
%times they are not. 
We plan to incorporate the highest voted answers in future work.
% We also
% applied the Bellon's clone agreement to 4 different combinations of
% the tools' configurations.  For disagreed clone pairs, we applied
% several filters to remove spurious and uninteresting clones.

% The number of online clones we found are subject to the clone
% detectors and their configurations.

% We also
% performed a pairwise matching between the default and EvaClone
% configurations of the two clone detection tools.

@@

%In addition, we are aware of voting mechanism in Stack Overflow and plan to
%incorporate highest-vote answers in the future work.

@@

Regarding the code snippets, we downloaded a full data dump and extracted Java
accepted answers since they are the most likely ones to be reused. Our findings
are limited to these restrictions. They may not be generalised to all
programming languages and all answers on Stack Overflow. We chose the curated
Qualitas corpus for Java open source projects containing 111 projects
\cite{QualitasCorpus}.  The projects span several areas of software and have
been used in several empirical
studies~\cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}. Although it
is a curated and well-established corpus, it may not fully represent all Java
open source software available. Lastly, we selected 130,703 GitHub Java projects
based on the number of stars they obtained to represent their popularity. They
might not represent all Java projects on GitHub, and the number of clone pairs
found may differ from other project selection criteria.

>>>>

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
\begin{abstract}
Online code clones are code fragments that are copied from software projects or
online sources to Stack Overflow as examples. Due to an absence of a checking
mechanism after the code has been copied to Stack Overflow, they can become
toxic code snippets, e.g.,~they suffer from being outdated or violating the
original software license. We present a study of online code clones on Stack
Overflow and their toxicity by incorporating two developer surveys and a
large-scale code clone detection. A survey of 201 high-reputation Stack Overflow
answerers (33\% response rate) showed that 131 participants (65\%) have ever
been notified of outdated code and 26 of them (20\%) rarely or never fix the
code. 138 answerers (69\%) never check for licensing conflicts between their
copied code snippets and Stack Overflow's CC BY-SA 3.0. A survey of 87 Stack
Overflow visitors shows that they experienced several issues from Stack Overflow
answers: mismatched solutions, outdated solutions, incorrect solutions, and buggy code. 
85\% of them are not aware of CC BY-SA 3.0
license enforced by Stack Overflow, and 66\% never check for license conflicts
when reusing code snippets. Our clone detection found online clone pairs between
72,365 Java code snippets on Stack Overflow and 111 open source projects in the
curated Qualitas corpus. We analysed 2,289 non-trivial online clone candidates.
Our investigation revealed strong evidence that 153 clones have been copied from
a Qualitas project to Stack Overflow. We found 100 of them (66\%) to be outdated,  
of which 10 were buggy and harmful for reuse.
Furthermore, we found 214 code snippets that
could potentially violate the license of their original software and appear 7,112
times in 2,427 GitHub projects.

@@

%The popularity of the Internet encourages tremendous amount of source code
% being shared online.
Stack Overflow is a popular online programming community with 7.6 million users,
14 million questions, and 23 million answers\footnote{Data as of 21 August 2017
	from~\url{https://stackexchange.com/sites}}. It allows programmers to ask
questions and give answers to programming problems. The website has found to be
useful for software
development~\cite{Ponzanelli2013,Ponzanelli2014,Keivanloo2014,Park2014,
	Stolee2014,Subramanian2013,Diamantopoulos2015,Treude2016} and also valuable for
educational purposes~\cite{Nasehi2012}. On Stack Overflow, each conversation
contains a question and a list of answers. The answers frequently contain at
least one code snippet as a solution to the question asked. We found that the
code snippets are often not authored directly on the Stack Overflow website
but copied from another location. A snippet in an answer could be copied and
modified from a code snippet in the question, copied from the answerer's own
code or from other locations including open source software (OSS) systems.

@@

Toxic code snippets mean code snippets that, after incorporating into software, degrade the software quality.
Stack Overflow code snippets
cloned from open source software or online sources can become toxic when they
are (1)~outdated, (2)~violating their original software
license, (3)~exhibiting code smells, (4)~containing faults, or (5)~having security vulnerabilities.
In this study, we focus on the first two forms of toxic code snippets, outdated code and license-violating code,
as these two problems are still underexplored compared to code smells~\cite{Tufano2015} and vulnerabilities~\cite{Acar2016,Fischer2017}.
Moreover, Stack Overflow users also express their concerns about these two problems
as shown in several discussion threads\footnote{Discussions about outdated answers and code license on
	Stack Overflow: meta.stackexchange.com/questions/131495, 
	meta.stackexchange.com/questions/11705/, meta.stackexchange.com/questions/12527,
	meta.stackexchange.com/questions/25956, meta.stackoverflow.com/questions/321291.}
	 on \textsf{meta.stackexchange.com} about outdated
answers and license of code on Stack Overflow.
Outdated code snippets can be harmful since they are not up-to-date with their originals and may
contain defects. Code snippets from open source projects usually fall under a
specific software license, e.g.,\ GNU General Public License (GPL). If they are
cloned to Stack Overflow answers without the license, and then flow to other projects
with conflicting licenses, legal issues may occur.

@@

	\item \textbf{An investigation of toxic code snippets on Stack Overflow:} Our study shows that from
	the 2,289 online clones, at least 328 have been copied from open source
	projects or external online sources to Stack Overflow, potentially violating
	software licenses. For 153 of them, we found evidence that they have been copied
	from a specific open source project. 
	100 of them were found to be outdated, of which 10 were buggy code.

@@

Moreover, using the information in git commit messages, we can associate each
change to its respective issues in an issue tracking system, such as Bugzilla or
Jira. We found that in 58 cases, the cloned code snippets on Stack Overflow were
changed because of a request in the issue tracking system. Since issue tracking
systems are also used, besides bug reports, for feature request and feature
enhancements, having an issue tracking ID can reflect that most of the changes are important
and not only a superficial fix such as code formatting. The intent behind
the changes are grouped into six categories as shown in \Cref{tab:intent_outdated}.
Enhancement is the majority intent accounting for 65 of the 100 outdated code (65\%). 
Next is code deprecation (15\%), which represents the code snippets that are outdated due to the use of
deprecated functions or APIs. The code snippets that we analysed contained a few deprecated code statements while
the newest version (based on the time we did the analysis) of the same code
snippets no longer contain the deprecated part.
There were 10 outdated code snippets (10\%) caused by bug fixing.
They contained buggy code statements, and were later fixed in the newest version.
The rest of the changes are because of code refactoring (6\%), changing coding style (3\%), and 
the data format change (2\%).
Not all outdated code is toxic. 
However, the 10 buggy and outdated code snippets we found are toxic and are harmful to reuse.

@@

\textbf{Internal validity:}

We applied different mechanisms to ensure the validity of the clone pairs we
classified.  First, we used two widely-used clone detection tools, Simian and
SourcererCC.  We tried five other clone detectors but could not add them to the
study due to their scalability issues and susceptibility to incomplete code
snippets. We adopted Bellon's agreement metric~\cite{Bellon2007} to merge clone
pairs for the manual classification and avoid double counting of the same clone
pairs. We studied the impact of choosing different thresholds for Bellon's clone agreement and the minimum clone
size of the two clone detectors and selected the optimal values.
Nevertheless, our study might still suffer from false negatives,
i.e.,~online code clones that are not reported by the tools or are filtered out
by the size (less than 10 lines) within the clone detection process. We selected
accepted answers on Stack Overflow in this study to focus on code snippets that
solve the question's problem and are often shown on top of the answer list.
We investigated the 72,365 Stack Overflow code snippets used in our study and
found that 62,245 of them (86\%) are also the highest voted answers.
We plan to incorporate the highest voted answers in future work.
We analysed the Stack Overflow data snapshot of January 2016. 
The findings may be different based on the newer snapshots. 
However, we do not expect large differences of the findings 
if we update the data set. The reason is that the Stack Overflow answers 
are rarely modified. Moreover, updating the dataset would eliminate the 
possibility to study the evolution of outdated answers.

@@

The detailed investigation of the 100 outdated answers on Stack Overflow may not
fully capture what Stack Overflow visitors actually do when they already expect
an outdated answer. However, our investigation tries to at least shade light on
this by comparing the popularity of the outdated answer and the newer answers
based on the number of votes. This may be affected by the duration that the
answers appear on a Stack Overflow post. The newer answers have less visibility
compared to the older answers.

@@

Regarding the code snippets, we downloaded a full data dump and extracted Java
accepted answers since they are the most likely ones to be reused. Our findings
are limited to these restrictions. They may not be generalised to all
programming languages and all answers on Stack Overflow. We chose the curated
Qualitas corpus for Java open source projects containing 111 projects
\cite{QualitasCorpus}. 
The projects span several areas of software and have been used in several empirical
studies~\cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}. Although it
is a curated and well-established corpus, it may not fully represent all Java
open source software available.

We selected 130,703 GitHub Java projects
based on the number of stars they obtained to represent their popularity. They
might not represent all Java projects on GitHub, and the number of clone pairs
found may differ from other project selection criteria.

Regarding the few number of toxic code snippets in Stack Overflow posts and code reuse in
GitHub, this is partially due to the data set of (only) 111 Java projects from
the Qualitas corpus. The clones (and the discovered outdated code and
potentially license-violating code snippets) reported in this paper are only
subject to these 111 projects. The number may increase if we expand the amount
of open source projects. Moreover, this study only focuses on Java, and the
situation may be worse or better for other programming languages.

### 2018-11-18 cloverflow-tse/cover_letter/second_round/cover_letter.tex
+ Updated the paper to reflect the response letter. + Small typo fix in the response letter. + Update a few wording in the response letter.

%\begin{abstract}
This paper is a journal-first submission to Transactions on Software Engineering. This is a minor revision the submission no.~TSE-2018-06-0228 and we would like to thank the anonymous reviewers for taking their time to read our paper carefully. With their useful and constructive reviews, we improved the work further as listed below and as discussed later in this letter.

@@

Regarding the few number of toxic code snippets in SO posts and code reuse in GitHub, this is partially due to the data set of (only) 111 Java projects from the Qualitas corpus. The clones (and the discovered outdated code and potentially license-violating code snippets) reported in this paper are only subject to these 111 projects. The number may increase if we expand the amount of open source projects. Moreover, this study only focuses on Java, and the situation may be worse or better for other programming languages. We have added this discussion into the Threats to Validity. \FIXME{To do}

@@

We have added this discussion in the Threats to Validity section \FIXME{To do}.

@@

The Deprecation intent partially indicates the cause of outdated code, but not all. It represents the code snippets that are outdated due to the use of deprecated functions or APIs. With this case of function/API deprecation, the code snippets that we analysed contained a few deprecated code statements while the newest version (based on the time we did the analysis) of the same code snippets no longer contain the deprecated part(s). The five other intents represent other cases of a code snippet being outdated. For example, the Bug intent represents a code snippet that previously contained buggy code statements, and was fixed in the newest version. The Refactoring intent represents a code snippet that was different from the newest version due to code refactoring.
To sum up, the table shows that outdated code can be caused by different intents and not all of them are harmful. Outdated code snippets with Bug intent are clearly harmful if they are posted on the Internet (e.g., Stack Overflow). We slightly modified the section explaining this table to be clearer \FIXME{To do}.

@@

Nonetheless, we have added a discussion of the age of the Stack Overflow data set to the Threats to Validity section \FIXME{To do}.

@@

``We found 100 of them (66\%) to be outdated. \textbf{Ten of them were buggy and harmful for reuse.} ''

@@

``100 of them were found to be outdated\textbf{, of which 10 were buggy code.}'' \FIXME{update in the paper}

@@

Again, we agree with your suggestion. The statement has been changed to ``We found that the code snippets are \textbf{often} not authored directly on the Stack Overflow website but copied from another location.''. \FIXME{update in the paper}

>>>>

%\begin{abstract}

This paper is a journal-first submission to Transactions on Software Engineering. This is a minor revision of the submission no.~TSE-2018-06-0228 and we would like to thank the anonymous reviewers for taking their time to read our paper carefully. With their useful and constructive reviews, we improved the work further as listed below and as discussed later in this letter.

@@

Regarding the few number of toxic code snippets in SO posts and code reuse in GitHub, this is partially due to the data set of (only) 111 Java projects from the Qualitas corpus. The clones (and the discovered outdated code and potentially license-violating code snippets) reported in this paper are only subject to these 111 projects. The number may increase if we expand the amount of open source projects. Moreover, this study only focuses on Java, and the situation may be worse or better for other programming languages. We have added this discussion into the Threats to Validity. \FIXME{Done}

@@

We have added this discussion in the Threats to Validity section \FIXME{Done}.

@@

The Deprecation intent partially indicates the cause of outdated code, but not all. It represents the code snippets that are outdated due to the use of deprecated functions or APIs. With this case of function/API deprecation, the code snippets that we analysed contained a few deprecated code statements while the newest version (based on the time we did the analysis) of the same code snippets no longer contain the deprecated part(s). The five other intents represent other cases of a code snippet being outdated. For example, the Bug intent represents a code snippet that previously contained buggy code statements, and were fixed in the newest version. The Refactoring intent represents a code snippet that was different from the newest version due to code refactoring.
To sum up, the table shows that outdated code can be caused by different intents and not all of them are harmful. Outdated code snippets with Bug intent are clearly harmful if they are posted on the Internet (e.g., Stack Overflow). We slightly modified the section explaining this table to be clearer \FIXME{Done}.

@@

Nonetheless, we have added a discussion of the age of the Stack Overflow data set to the Threats to Validity section \FIXME{Done}.

@@

``We found 100 of them (66\%) to be outdated,  \textbf{of which 10 were buggy and harmful for reuse.}''

@@

``100 of them were found to be outdated\textbf{, of which 10 were buggy code.}'' \FIXME{Done}

@@

Again, we agree with your suggestion. The statement has been changed to ``We found that the code snippets are \textbf{often} not authored directly on the Stack Overflow website but copied from another location.''. \FIXME{Done}
